Chemical tagging can work: \\ Identification of stellar phase-space structures \\ purely by chemical-abundance similarity

### 2016-01-18 papers/clusters.tex
Minor changes, incl. a question

% For the training data labels (used to train \thecannon; see below), we
% use the \apogee\ \acronym{DR12} \aspcap\ atmospheric parameters and
% 15-element abundances, but only for the subset of ARC:XXXXX red-giant
% stars that have spectral signal-to-noise ratio measurements greater
% than 200.
% This is a small fraction of the total sample, but these highest
% signal-to-noise stars are observed to obtain consistent, low-scatter,
% sensible abundance-space measurements.

@@

% In the second stage---the test step---each unlabeled star is used to
% establish a single-star likelihood function for labels, holding the
% coefficients fixed.
% \thecannon\ finds the labels that minimize the single-star likelihood
% function for each test-set star.
% This optimization is not convex, but it is embarrassingly parallel.
% For the results shown here, the training step takes hours and the test
% step takes less than an hour on a small research cluster in Cambridge.

@@

@@

One note on clustering algorithm decisions is warranted:
Because this project is just a demonstration of the chemical-tagging
concept, there is no requirement that we choose the best clustering
algorithm or the method that reveals the best structures.
Indeed, it is a feature of this work that even the simplest, most
generic, least tuned clustering algorithm returns interesting
structures (as shown below).
The prospects for Milky Way science only improve as the clustering
algorithm improves.

>>>>

% For the training data labels (used to train \thecannon; see below), we
% use the \apogee\ \acronym{DR12} \aspcap\ atmospheric parameters and
% 15-element abundances, but only for the subset of 12,681 red-giant
% stars that have spectral signal-to-noise ratio measurements greater
% than 200.
% This is a small fraction of the total sample, but these highest
% signal-to-noise stars are observed to obtain consistent, low-scatter,
% sensible abundance-space measurements.

@@

% In the second stage---the test step---each unlabeled star is used to
% establish a single-star likelihood function for labels, holding the
% coefficients fixed.
% \thecannon\ finds the labels that minimize the single-star likelihood
% function for each test-set star.
% This optimization is not convex, but it is embarrassingly parallel.
% For the results shown here, the training step takes hours and the test
%step for 150,000 spectra takes less than 30~minutes on a small 
%research cluster in Cambridge.

@@

% ARC asks: how did you chose the initializations?

@@

One note on clustering algorithm decisions is warranted:
Because this project is just a demonstration of the chemical-tagging
concept, there is no requirement that we choose the best clustering
algorithm or the method that reveals the best structures.
Indeed, it is a feature of this work that even the simplest, most
generic, least-tuned clustering algorithm returns interesting
structures (as shown below).
The prospects for Milky Way science only improve as the clustering
algorithm improves.
